Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-22 graph_housing_exp1_distr_8_5.tex
Change all plots from probability to probability density

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$H$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0000) (1.9204,0.3850,0.0000) (1.9204,0.4405,0.0000) (1.1296,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4405,0.0000) (1.9204,0.4405,0.0000) (1.9204,0.4860,0.0000) (1.1296,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4860,0.0000) (1.9204,0.4860,0.0000) (1.9204,0.4910,0.0000) (1.1296,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (1.9204,0.4910,0.0000) (1.9204,0.4960,0.0000) (1.1296,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (1.9204,0.4960,0.0000) (1.9204,0.5190,0.0000) (1.1296,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5190,0.0000) (1.9204,0.5190,0.0000) (1.9204,0.5220,0.0000) (1.1296,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5220,0.0000) (1.9204,0.5220,0.0000) (1.9204,0.5280,0.0000) (1.1296,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5280,0.0000) (1.9204,0.5280,0.0000) (1.9204,0.5410,0.0000) (1.1296,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0000) (1.9204,0.5410,0.0000) (1.9204,0.5455,0.0000) (1.1296,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5455,0.0025) (1.9204,0.5455,0.0025) (1.9204,0.5910,0.0025) (1.1296,0.5910,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5910,0.0425) (1.9204,0.5910,0.0425) (1.9204,0.6390,0.0425) (1.1296,0.6390,0.0425)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0065) (1.9204,0.6390,0.0065) (1.9204,0.6510,0.0065) (1.1296,0.6510,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1040) (1.9204,0.6510,0.1040) (1.9204,0.8205,0.1040) (1.1296,0.8205,0.1040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0300) (1.9204,0.8205,0.0300) (1.9204,0.8710,0.0300) (1.1296,0.8710,0.0300)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.3850,0.0000) (2.5884,0.3850,0.0000) (2.5884,0.4405,0.0000) (1.9204,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4405,0.0000) (2.5884,0.4405,0.0000) (2.5884,0.4860,0.0000) (1.9204,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4860,0.0000) (2.5884,0.4860,0.0000) (2.5884,0.4910,0.0000) (1.9204,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.9204,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5190,0.0000) (1.9204,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5190,0.0085) (2.5884,0.5190,0.0085) (2.5884,0.5220,0.0085) (1.9204,0.5220,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5220,0.0000) (2.5884,0.5220,0.0000) (2.5884,0.5280,0.0000) (1.9204,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5280,0.0000) (2.5884,0.5280,0.0000) (2.5884,0.5410,0.0000) (1.9204,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5410,0.0025) (2.5884,0.5410,0.0025) (2.5884,0.5455,0.0025) (1.9204,0.5455,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5455,0.0580) (2.5884,0.5455,0.0580) (2.5884,0.5910,0.0580) (1.9204,0.5910,0.0580)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5910,0.0485) (2.5884,0.5910,0.0485) (2.5884,0.6390,0.0485) (1.9204,0.6390,0.0485)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6390,0.0120) (2.5884,0.6390,0.0120) (2.5884,0.6510,0.0120) (1.9204,0.6510,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6510,0.0665) (2.5884,0.6510,0.0665) (2.5884,0.8205,0.0665) (1.9204,0.8205,0.0665)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.8205,0.0000) (2.5884,0.8205,0.0000) (2.5884,0.8710,0.0000) (1.9204,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0000) (3.0793,0.3850,0.0000) (3.0793,0.4405,0.0000) (2.5884,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4405,0.0000) (3.0793,0.4405,0.0000) (3.0793,0.4860,0.0000) (2.5884,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4860,0.0115) (3.0793,0.4860,0.0115) (3.0793,0.4910,0.0115) (2.5884,0.4910,0.0115)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0000) (3.0793,0.4910,0.0000) (3.0793,0.4960,0.0000) (2.5884,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0160) (3.0793,0.4960,0.0160) (3.0793,0.5190,0.0160) (2.5884,0.5190,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5190,0.0065) (3.0793,0.5190,0.0065) (3.0793,0.5220,0.0065) (2.5884,0.5220,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5220,0.0000) (3.0793,0.5220,0.0000) (3.0793,0.5280,0.0000) (2.5884,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5280,0.0000) (3.0793,0.5280,0.0000) (3.0793,0.5410,0.0000) (2.5884,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0040) (3.0793,0.5410,0.0040) (3.0793,0.5455,0.0040) (2.5884,0.5455,0.0040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5455,0.0250) (3.0793,0.5455,0.0250) (3.0793,0.5910,0.0250) (2.5884,0.5910,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5910,0.0000) (3.0793,0.5910,0.0000) (3.0793,0.6390,0.0000) (2.5884,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0000) (3.0793,0.6390,0.0000) (3.0793,0.6510,0.0000) (2.5884,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0250) (3.0793,0.6510,0.0250) (3.0793,0.8205,0.0250) (2.5884,0.8205,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (3.0793,0.8205,0.0000) (3.0793,0.8710,0.0000) (2.5884,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.3850,0.0100) (4.4802,0.3850,0.0100) (4.4802,0.4405,0.0100) (3.0793,0.4405,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4405,0.0495) (4.4802,0.4405,0.0495) (4.4802,0.4860,0.0495) (3.0793,0.4860,0.0495)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4860,0.0345) (4.4802,0.4860,0.0345) (4.4802,0.4910,0.0345) (3.0793,0.4910,0.0345)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4910,0.0000) (4.4802,0.4910,0.0000) (4.4802,0.4960,0.0000) (3.0793,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4960,0.0425) (4.4802,0.4960,0.0425) (4.4802,0.5190,0.0425) (3.0793,0.5190,0.0425)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5190,0.0000) (4.4802,0.5190,0.0000) (4.4802,0.5220,0.0000) (3.0793,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5220,0.0000) (4.4802,0.5220,0.0000) (4.4802,0.5280,0.0000) (3.0793,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5280,0.0525) (4.4802,0.5280,0.0525) (4.4802,0.5410,0.0525) (3.0793,0.5410,0.0525)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5410,0.0155) (4.4802,0.5410,0.0155) (4.4802,0.5455,0.0155) (3.0793,0.5455,0.0155)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5455,0.0135) (4.4802,0.5455,0.0135) (4.4802,0.5910,0.0135) (3.0793,0.5910,0.0135)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5910,0.0000) (4.4802,0.5910,0.0000) (4.4802,0.6390,0.0000) (3.0793,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6390,0.0000) (4.4802,0.6390,0.0000) (4.4802,0.6510,0.0000) (3.0793,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6510,0.0000) (4.4802,0.6510,0.0000) (4.4802,0.8205,0.0000) (3.0793,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.8205,0.0000) (4.4802,0.8205,0.0000) (4.4802,0.8710,0.0000) (3.0793,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.3850,0.0080) (4.7503,0.3850,0.0080) (4.7503,0.4405,0.0080) (4.4802,0.4405,0.0080)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4405,0.0035) (4.7503,0.4405,0.0035) (4.7503,0.4860,0.0035) (4.4802,0.4860,0.0035)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4860,0.0000) (4.7503,0.4860,0.0000) (4.7503,0.4910,0.0000) (4.4802,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4910,0.0100) (4.7503,0.4910,0.0100) (4.7503,0.4960,0.0100) (4.4802,0.4960,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4960,0.0000) (4.7503,0.4960,0.0000) (4.7503,0.5190,0.0000) (4.4802,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5190,0.0000) (4.7503,0.5190,0.0000) (4.7503,0.5220,0.0000) (4.4802,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5220,0.0000) (4.7503,0.5220,0.0000) (4.7503,0.5280,0.0000) (4.4802,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5280,0.0060) (4.7503,0.5280,0.0060) (4.7503,0.5410,0.0060) (4.4802,0.5410,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5410,0.0000) (4.7503,0.5410,0.0000) (4.7503,0.5455,0.0000) (4.4802,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5455,0.0000) (4.7503,0.5455,0.0000) (4.7503,0.5910,0.0000) (4.4802,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5910,0.0000) (4.7503,0.5910,0.0000) (4.7503,0.6390,0.0000) (4.4802,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6390,0.0000) (4.7503,0.6390,0.0000) (4.7503,0.6510,0.0000) (4.4802,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6510,0.0000) (4.7503,0.6510,0.0000) (4.7503,0.8205,0.0000) (4.4802,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.8205,0.0000) (4.7503,0.8205,0.0000) (4.7503,0.8710,0.0000) (4.4802,0.8710,0.0000)};

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=H,
			ylabel=E,
			colorbar,
			point meta min=0, point meta max=1.0,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.2,...,1.01},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.000000) (1.9204,0.3850,0.000000) (1.9204,0.4405,0.0000) (1.1296,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4405,0.000000) (1.9204,0.4405,0.000000) (1.9204,0.4860,0.0000) (1.1296,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4860,0.000000) (1.9204,0.4860,0.000000) (1.9204,0.4910,0.0000) (1.1296,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.000000) (1.9204,0.4910,0.000000) (1.9204,0.4960,0.0000) (1.1296,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.000000) (1.9204,0.4960,0.000000) (1.9204,0.5190,0.0000) (1.1296,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5190,0.000000) (1.9204,0.5190,0.000000) (1.9204,0.5220,0.0000) (1.1296,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5220,0.000000) (1.9204,0.5220,0.000000) (1.9204,0.5280,0.0000) (1.1296,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5280,0.000000) (1.9204,0.5280,0.000000) (1.9204,0.5410,0.0000) (1.1296,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.000000) (1.9204,0.5410,0.000000) (1.9204,0.5455,0.0000) (1.1296,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5455,0.006948) (1.9204,0.5455,0.006948) (1.9204,0.5910,0.0069) (1.1296,0.5910,0.0069)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5910,0.111972) (1.9204,0.5910,0.111972) (1.9204,0.6390,0.1120) (1.1296,0.6390,0.1120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.068500) (1.9204,0.6390,0.068500) (1.9204,0.6510,0.0685) (1.1296,0.6510,0.0685)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.077593) (1.9204,0.6510,0.077593) (1.9204,0.8205,0.0776) (1.1296,0.8205,0.0776)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.075126) (1.9204,0.8205,0.075126) (1.9204,0.8710,0.0751) (1.1296,0.8710,0.0751)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.3850,0.000000) (2.5884,0.3850,0.000000) (2.5884,0.4405,0.0000) (1.9204,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4405,0.000000) (2.5884,0.4405,0.000000) (2.5884,0.4860,0.0000) (1.9204,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4860,0.000000) (2.5884,0.4860,0.000000) (2.5884,0.4910,0.0000) (1.9204,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4910,0.000000) (2.5884,0.4910,0.000000) (2.5884,0.4960,0.0000) (1.9204,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4960,0.000000) (2.5884,0.4960,0.000000) (2.5884,0.5190,0.0000) (1.9204,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5190,0.424152) (2.5884,0.5190,0.424152) (2.5884,0.5220,0.4242) (1.9204,0.5220,0.4242)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5220,0.000000) (2.5884,0.5220,0.000000) (2.5884,0.5280,0.0000) (1.9204,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5280,0.000000) (2.5884,0.5280,0.000000) (2.5884,0.5410,0.0000) (1.9204,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5410,0.083167) (2.5884,0.5410,0.083167) (2.5884,0.5455,0.0832) (1.9204,0.5455,0.0832)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5455,0.190827) (2.5884,0.5455,0.190827) (2.5884,0.5910,0.1908) (1.9204,0.5910,0.1908)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5910,0.151260) (2.5884,0.5910,0.151260) (2.5884,0.6390,0.1513) (1.9204,0.6390,0.1513)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6390,0.149701) (2.5884,0.6390,0.149701) (2.5884,0.6510,0.1497) (1.9204,0.6510,0.1497)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6510,0.058732) (2.5884,0.6510,0.058732) (2.5884,0.8205,0.0587) (1.9204,0.8205,0.0587)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.8205,0.000000) (2.5884,0.8205,0.000000) (2.5884,0.8710,0.0000) (1.9204,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.000000) (3.0793,0.3850,0.000000) (3.0793,0.4405,0.0000) (2.5884,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4405,0.000000) (3.0793,0.4405,0.000000) (3.0793,0.4860,0.0000) (2.5884,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4860,0.468479) (3.0793,0.4860,0.468479) (3.0793,0.4910,0.4685) (2.5884,0.4910,0.4685)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.000000) (3.0793,0.4910,0.000000) (3.0793,0.4960,0.0000) (2.5884,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.141695) (3.0793,0.4960,0.141695) (3.0793,0.5190,0.1417) (2.5884,0.5190,0.1417)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5190,0.441321) (3.0793,0.5190,0.441321) (3.0793,0.5220,0.4413) (2.5884,0.5220,0.4413)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5220,0.000000) (3.0793,0.5220,0.000000) (3.0793,0.5280,0.0000) (2.5884,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5280,0.000000) (3.0793,0.5280,0.000000) (3.0793,0.5410,0.0000) (2.5884,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.181055) (3.0793,0.5410,0.181055) (3.0793,0.5455,0.1811) (2.5884,0.5455,0.1811)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5455,0.111916) (3.0793,0.5455,0.111916) (3.0793,0.5910,0.1119) (2.5884,0.5910,0.1119)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5910,0.000000) (3.0793,0.5910,0.000000) (3.0793,0.6390,0.0000) (2.5884,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.000000) (3.0793,0.6390,0.000000) (3.0793,0.6510,0.0000) (2.5884,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.030042) (3.0793,0.6510,0.030042) (3.0793,0.8205,0.0300) (2.5884,0.8205,0.0300)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.000000) (3.0793,0.8205,0.000000) (3.0793,0.8710,0.0000) (2.5884,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.3850,0.012861) (4.4802,0.3850,0.012861) (4.4802,0.4405,0.0129) (3.0793,0.4405,0.0129)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4405,0.077655) (4.4802,0.4405,0.077655) (4.4802,0.4860,0.0777) (3.0793,0.4860,0.0777)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4860,0.492523) (4.4802,0.4860,0.492523) (4.4802,0.4910,0.4925) (3.0793,0.4910,0.4925)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4910,0.000000) (4.4802,0.4910,0.000000) (4.4802,0.4960,0.0000) (3.0793,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4960,0.131898) (4.4802,0.4960,0.131898) (4.4802,0.5190,0.1319) (3.0793,0.5190,0.1319)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5190,0.000000) (4.4802,0.5190,0.000000) (4.4802,0.5220,0.0000) (3.0793,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5220,0.000000) (4.4802,0.5220,0.000000) (4.4802,0.5280,0.0000) (3.0793,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5280,0.288266) (4.4802,0.5280,0.288266) (4.4802,0.5410,0.2883) (3.0793,0.5410,0.2883)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5410,0.245865) (4.4802,0.5410,0.245865) (4.4802,0.5455,0.2459) (3.0793,0.5455,0.2459)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5455,0.021179) (4.4802,0.5455,0.021179) (4.4802,0.5910,0.0212) (3.0793,0.5910,0.0212)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5910,0.000000) (4.4802,0.5910,0.000000) (4.4802,0.6390,0.0000) (3.0793,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6390,0.000000) (4.4802,0.6390,0.000000) (4.4802,0.6510,0.0000) (3.0793,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6510,0.000000) (4.4802,0.6510,0.000000) (4.4802,0.8205,0.0000) (3.0793,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.8205,0.000000) (4.4802,0.8205,0.000000) (4.4802,0.8710,0.0000) (3.0793,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.3850,0.053387) (4.7503,0.3850,0.053387) (4.7503,0.4405,0.0534) (4.4802,0.4405,0.0534)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4405,0.028490) (4.7503,0.4405,0.028490) (4.7503,0.4860,0.0285) (4.4802,0.4860,0.0285)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4860,0.000000) (4.7503,0.4860,0.000000) (4.7503,0.4910,0.0000) (4.4802,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4910,0.740741) (4.7503,0.4910,0.740741) (4.7503,0.4960,0.7407) (4.4802,0.4960,0.7407)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4960,0.000000) (4.7503,0.4960,0.000000) (4.7503,0.5190,0.0000) (4.4802,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5190,0.000000) (4.7503,0.5190,0.000000) (4.7503,0.5220,0.0000) (4.4802,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5220,0.000000) (4.7503,0.5220,0.000000) (4.7503,0.5280,0.0000) (4.4802,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5280,0.170940) (4.7503,0.5280,0.170940) (4.7503,0.5410,0.1709) (4.4802,0.5410,0.1709)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5410,0.000000) (4.7503,0.5410,0.000000) (4.7503,0.5455,0.0000) (4.4802,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5455,0.000000) (4.7503,0.5455,0.000000) (4.7503,0.5910,0.0000) (4.4802,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5910,0.000000) (4.7503,0.5910,0.000000) (4.7503,0.6390,0.0000) (4.4802,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6390,0.000000) (4.7503,0.6390,0.000000) (4.7503,0.6510,0.0000) (4.4802,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6510,0.000000) (4.7503,0.6510,0.000000) (4.7503,0.8205,0.0000) (4.4802,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.8205,0.000000) (4.7503,0.8205,0.000000) (4.7503,0.8710,0.0000) (4.4802,0.8710,0.0000)};
